---
title: "**Homework 2023-03-07**"
author: "Jesse"
date: "2023-03-07"
output: 
  prettydoc:html_pretty
    theme:tactile
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE,
                      error=FALSE,
                      fig.path="../Output/") #saves it to this destination file
```
#### Last edited - 2023-03-09
# Plot

```{r HomeworkPlot, include=TRUE, fig.align='center', echo=FALSE}
#Load libraries
library(tidyverse)
library(here)
library(maps)
library(mapdata)
library(mapproj)
library(stringr)
world=map_data("world") #create a function that includes the requisite data to create a plot of the world
plastics_pepsi <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-26/plastics.csv') #create a function that loads the tidytuesday csv on plastic collections
plastics_graph <- plastics_pepsi %>% #new data frame for manipulation of data
  mutate(region=case_when(country=="United States of America" ~ "USA", #add "regions" column and rename these countries in accord with my world data
                          country=="United Kingdom of Great Britain & Northern Ireland"~"UK",
                          country=="United Kingdom"~"UK",
                          country=="Korea"~"South Korea",
                          country=="Hong Kong"~"China",
                          TRUE ~as.character(plastics_pepsi$country))) %>% 
  
  mutate(company=tolower(parent_company)) %>% #make the parent_company data lowercase because some pepsi data has different casing
  
  filter(company=="pepsico") #filter by pepsico
world_new <- world %>% #create a function that loads the world dataframe
  full_join(plastics_graph) %>% #combine all data between plastics_graph and world data
  summarise(company, region, lat, long, group, grand_total, order) #only include these columns

ggplot()+ #create a plot
  geom_polygon(data=world_new, aes(group=group, x=long, y=lat, fill=grand_total), color="orange1")+ #plot polygons to form a map of the world using these aesthetics
  scale_fill_viridis_c(trans="log2")+ #use continuos colors and represent the difference in grand_total as log base 2 values
  theme_void()+ #change the theme of the plot so I can customize the background
  theme(panel.background=element_rect(fill="lightblue"))+ #make the background light blue
  labs(title="PepsiCo Plastics Collected Per Country", #create plot title
       fill="Log_2 of Total Plastics 
       Collected Per Country", #rename the "fill" legend for grand_total
       caption="Hong Kong's plastics attributed to China as a whole; North Korea's plastics as a whole attributed to only South Korea 
(the plastics data set did not draw a difference between these national entities)")+ #create a caption with this text
ggsave(here("Week_07","Output","Homework_Map.pdf"),
       width=9.5, height=5)#save to the appropriate location