---
title: "**Homework 2023-03-07**"
author: "Jesse"
date: "2023-03-07"
output: 
  prettydoc:html_pretty
    theme:tactile
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE,
                      error=FALSE,
                      fig.path="../Output/") #saves it to this destination file
```

# Plot

```{r HomeworkPlot, include=TRUE, fig.align='center', echo=FALSE}
library(tidyverse)
library(here)
library(maps)
library(mapdata)
library(mapproj)
library(stringr)

plastics_lower <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-26/plastics.csv') %>% 
  mutate(region=tolower(country))
world=map_data("world")
view(plastics_lower)

setdiff(plastics_pepsi$region,world_lower$region)

setdiff(world_lower$region,plastics$region)
setdiff(plastics_graph$country, world$region)

world_lower <- map_data("world") %>% 
  mutate(region=tolower(region))



plastics_pepsi <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-26/plastics.csv') 
view(plastics_pepsi)
plastics_graph <- plastics_pepsi%>%
  mutate(region=case_when(country=="United States of America"~"USA",
                         country=="United Kingdom of Great Britain & Northern Ireland"~"UK",
                         country=="United Kingdom"~"UK",
                         country=="Korea"~"South Korea",
                         country=="Hong Kong"~"China",
                         TRUE ~as.character(plastics_pepsi$country))) %>% 
  
  mutate(company=tolower(parent_company)) %>%
  
  filter(company=="pepsico") %>% 
  
  full_join(world) %>% 
 
   summarise(company, region, lat, long, group, grand_total, order)

view(plastics_graph)

ggplot()+
  geom_polygon(data=plastics_graph, aes(group=group, x=long, y=lat, fill=grand_total), color="orange")+
  
  scale_fill_gradient(trans="log2")+
theme_void()+
theme(panel.background=element_rect(fill="lightblue"))+
  ggsave(here("Week_07","Output","Lecture_Map.pdf"))
ggsave(here("Week_07","Output","Homework_Map.pdf"))
